---
title: "conf.dectct_learning_note"
author: "Chun Hsien Wu"
date: '2022-09-17'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Using sirt package and conf.detect function to analysis item dimensionality
```{r}
library(sirt)
# load TIMMS data
data(data.timss)
# extract data
dat <- data.timss$data
```
Now, to check data matrix
```{r}
dim(dat)
# and take a look at the first examinees
head(dat)
# take out examinees responses matrix
dat <- dat[, substring( colnames(dat),1,1)=="M" ]
```
extract item information
```{r}
# extract item informations
iteminfo <- data.timss$item
iteminfo
```
#### estimate using Rasch model
```{r,attr.output='style="max-height: 100px;"'}
mod1 <- sirt::rasch.mml2( dat )
```

The classification scheme of these indices are as follows (Jang & Roussos, 2007; Zhang, 2007):

Strong multidimensionality 	DETECT > 1.00

Moderate multidimensionality 	.40 < DETECT < 1.00

Weak multidimensionality 	.20 < DETECT < .40

Essential unidimensionality 	DETECT < .20

Maximum value under simple structure 	ASSI=1 	RATIO=1

Essential deviation from unidimensionality 	ASSI > .25 	RATIO
> .36

Essential unidimensionality 	ASSI < .25 	RATIO < .36 

#### estimated WLEs
```{r}
wle1 <- sirt::wle.rasch( dat, b=mod1$item$b )$theta
```
#### detect for domains
Now, using conf.detect function to detect for cognitive domains
```{r}
detect1 <- sirt::conf.detect( data=dat, score=wle1,
                    itemcluster=iteminfo$Content.Domain )
```
#### Exploratory DETECT: Application of a cluster analysis employing the Ward method
```{r}
detect5 <- sirt::expl.detect( data=dat, score=wle1,
                nclusters=10, N.est=nrow(dat)  )
```
#### # Plot cluster solution
```{r}
pl <- graphics::plot( detect5$clusterfit, main="Cluster solution" )
stats::rect.hclust(detect5$clusterfit, k=4, border="red")
```

