---
title: "Multidimensional Rasch model in mirt"
author: "Chun Hsien Wu"
date: "2021年9月8日"
output: html_document
---

## Multidimensional Rasch Model


```{r}
library("hemp")
library("mirt")
```
```{r}
mrasch_mod <- "F1 = 1 - 6, 13 - 21, 23 - 24
               F2 = 7 - 20, 22 - 24
               COV = F1 * F2"
```
```{r}
mrasch_fit <- mirt(data = mimic, model = mrasch_mod,
                       itemtype = "Rasch", SE = TRUE, verbose = FALSE)
```
```{r}
mrasch_params <- coef(mrasch_fit, simplify = TRUE)
mrasch_params$items
```

Item 13-20, 23 and 24 has a non-zero item discrimination parameter for both a1 and a2 because this particular item is associated with both F1 and F2.

Column d represents the estimated intercept parameter for the items. G and u are the lower asymptote (ie., guessing) and upper asymptote parameters.

```{r}
mrasch_items <-data.frame(MDISC(mrasch_fit),MDIFF(mrasch_fit))
```
```{r}
colnames(mrasch_items) <- c("mrasch_mdisc", "mrasch_diff")
mrasch_items
```

Finally, the authour print the estimated variance-covariance matrix of the two latent traits.
```{r}
mrasch_params$cov
```

The output shows that the variances of  F1 and F2 are 0.689 and 0.738, respectively. The covariance of the two latent traits is 0.34.

Now, we can check the item and test characteristics visually using the itemplot and plot functions.
```{r}
itemplot(mrasch_fit, type = "trace", item =13)
itemplot(mrasch_fit, type = "tracecontour", item =13)
```
Type ="trace" means we can create an item characteristic surface plot, Type= "tracecontour" means we can create an item countour plot.
```{r}
plot(mrasch_fit, type="info")
plot(mrasch_fit, type="SE")
plot(mrasch_fit, type="score")
```

