---
title: "Between-Item MIRT model estimation"
author: "Chun Hsien Wu"
date: '2022-09-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### two dimensional Between-Item MIRT model
frist, set random seed

```{r}
rm(list=ls())
set.seed(9776)
```         
set sample size, define item difficulties and length of items
```{r}
N <- 3400
f0 <- c( .5, .25, -.25, -.5, 0, -.5, -.25, .25, .5, 0 )
I <- length(f0)
```
belod coding shows:define loadings

From f1, we can see that item 1 to 5 belong to first dimension, and item 6 to 10 belong to second dimension.
```{r}
f1 <- matrix( 0, I, 2 )
f1[ 1:5,1] <- c(.8,.7,.6,.5, .5)
f1[ 6:10,2] <- c(.8,.7,.6,.5, .5 )
f1
```
Setting theta's covariance matrix and simulate thetas
```{r}
Pval <- matrix( c(1,.5,.5,1), 2, 2 )
# simulate theta
library(mvtnorm)
theta <- mvtnorm::rmvnorm(N, mean=c(0,0), sigma=Pval )
```
Let's see how thetas distribute
```{r}
plot(theta)
```
simulate item responses
```{r}
dat <- matrix( NA, N, I )
for (ii in 1:I){ # ii <- 1
    dat[,ii] <- 1*( stats::pnorm(f0[ii]+theta[,1]*f1[ii,1]+theta[,2]*f1[ii,2])>
                     stats::runif(N) )
        }
colnames(dat) <- paste0("I", 1:I)
dim(dat)
head(dat)
```
Add item cluster, learn from conf.detect: Confirmatory DETECT  
```{r}
itemcluster <- c( rep(1,5), rep(2,I-5) )
```
 From f1, I can realize this simulated data is generated under between item MIRT model.
 
Now try to fit conf.detect function
```{r}
# estimate Rasch model
mod1 <- sirt::rasch.mml2( dat )
# estimate WLEs
wle1 <- sirt::wle.rasch( dat, b=mod1$item$b )$theta
```

DETECT for content domains
```{r}
detect1 <- sirt::conf.detect( data=dat, score=wle1,
                    itemcluster= itemcluster )
```

Exploratory DETECT: Application of a cluster analysis employing the Ward method

```{r}
detect2 <- sirt::expl.detect( data=dat, score=wle1,
                nclusters=10, N.est=nrow(dat)  )
```